---
title: "Prediction Assignment Writeup"
author: "Brittany Duke"
date: "February 8, 2019"
output: html_document
---

The purpose of this assignment is to predict the manner in which people did the exercise.

The data for this assignment comes from the following source: http://groupware.les.inf.puc-rio.br/har.

## Pre-processing Data

```{r}
library(caret)
set.seed(12463)
training <- read.csv("pml-training.csv", stringsAsFactors=FALSE)
training$classe <- as.factor(training$classe)
training <- training[,-nearZeroVar(training)]
training <- training[,-c(1,2,3,4,5,6,7)]
```

```{r}
inTrain <- createDataPartition(y=training$classe, p=0.75, list=FALSE)
training <- training[inTrain,]
testing <- training[-inTrain,]
preObj <- preProcess(training[,-length(training)],method=c("center", "scale", "knnImpute", "pca"), thresh=0.9)
clean_data <- predict(preObj,training[,-length(training)])
```

## Prediction

After getting the clean data set from the above processing, we use Knn method to build model. We use testing data to evaluate the performance of our model. 
The accuracy is 0.9748. 

```{r}
modelFit <- train(training$classe ~.,data=clean_data, method="knn")
test <- predict(preObj, testing[,-length(testing)])
confusionMatrix(testing$classe, predict(modelFit,test))
```


Finally, we load the testing data file and predict the following result:
```{r}
testing <- read.csv("pml-testing.csv", stringsAsFactors=FALSE)
testing <- testing[,names(testing) %in% names(training)]
test <- predict(preObj, testing)
predict_result <- predict(modelFit, test)
```
